Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-07-01 doc/paper-lcr.tex
bit more lit

The first attempts at reconstructing the line of sight mass distribution in
strong lens fields were \ldots. \flag{More needed here. Previous work on
environments: Keeton, Zabludoff, Auger, Momcheva, Wong, others. Spectroscopic
surveys, modelling mass along line of sight.}

These observational investigations provided useful insight into the problem. 
Coming from the opposite direction, \citet{Hilbert++2009} performed ray-tracing
experiments through the Millenium Simulation, generating a predicted $\xkappa$
at every position in a simulated sky. The first step towards using this
excellent calibration resource was taken by \citet{Suyu++2010}, who selected
Millenium lines of sight that a) were found to contain a strong lens and b) had
comparable apparent galaxy overdensity in a 45 arcsec radius aperture down to $i
< 24$. This overdensity could be compared to the overdensity of the B1608$+$656
line of sight \citep{Fass+Koop2010}, and hence an estimate of the probability
density function (PDF) $\Pr(\xkappa)$ could be made. This PDF is the key
quantity for any ensemble analysis, since by marginalising over it we can
correctly propagate the uncertainties due to weak lensing by line of sight mass
structure.

In this paper we use the Millenium Simulation mock galaxy catalogs and
ray-traced lensing effects to test the accuracy of line of sight mass
reconstructions. Probabilistically ssigning mass and redshift to every observed
galaxy in the field around a time delay lens, we generate Monte Carlo sample
line of sight mass distributions, and estimate the external convergence due to
each one. This gives us a $\Pr(\xkappa)$ that can be propagated into further
joint inferences. We focus on time delay lens cosmography, and quantify our
results in terms of the uncertainty on the mean time delay distance to a test
sample of $N$ lenses (where for clarity each lens has the same deflector and
source redshift, and the same lens model and time delay uncertainty).

>>>>

Previous attempts at reconstructing the line of sight mass distribution in
strong lens fields have focused on spectroscopic surveys to ascertain group
membership, and on understanding the external shear apparently required by the
strong lens models.  The probability density function (PDF) $\Pr(\xkappa)$ is
the target for any reconstruction analysis, and the key quantity for any
ensemble analysis, since by marginalising over it we can correctly propagate
the uncertainties due to weak lensing by line of sight mass structure. 
\flag{More needed here. Previous work on environments: Keeton, Zabludoff,
Auger, Momcheva, Wong, others.} Most recently, \citet{Wong++2011} ran Monte
Carlo reconstructions of the mass in nine lens fields, and compared the
resulting predicted shear distributions with the lens model external shear.
Their simulations show most of  the shear being generated by bright galaxies
within 2~arcminutes of the lens, and that both line of sight structures and
the group of galaxies in each lens plane contribute significant proportions of
the shear. The significant discrepancies between the lens model shear and the
Monte Carlo predictions are attributed to both the environment modelling and
the strong lens modelling itself.

These observational investigations have provided very useful insight into the
problem.  Coming from the opposite direction, large numerical simulations have
been used to predict, from first principles the distribution of likely
external shears and convergences along strong lens lines of sight. \flag{More
needed here. Holder \& Schechter, Dalal \& Watson}. \citet{Hilbert++2009}
performed ray-tracing experiments through the Millenium Simulation, generating
a predicted $\xkappa$ at every position in a simulated sky. The first step
towards using this excellent calibration resource was taken by
\citet{Suyu++2010}, who selected Millenium lines of sight that a) were found
to contain a strong lens and b) had comparable apparent galaxy overdensity in
a 45 arcsec radius aperture down to $i < 24$. This overdensity could be
compared to the overdensity of the B1608$+$656 line of sight
\citep{Fass+Koop2010}, and hence an estimate of  $\Pr(\xkappa)$ could be
made.

What has not been investigated before, but is the subject of this paper, is
the use of simulations to {\it calibrate} lightcone reconstruction methods.
Ray-tracing through the simulations gives a ``truth'' that we can attempt to
recover.  In this paper we use the Millenium Simulation mock galaxy catalogs
and ray-traced lensing effects to test the accuracy of line of sight mass
reconstructions. Probabilistically ssigning mass and redshift to every
observed galaxy in the field around a time delay lens, we generate Monte Carlo
sample line of sight mass distributions, and estimate the external convergence
due to each one. This gives us a $\Pr(\xkappa)$ that can be propagated into
further joint inferences. We focus on time delay lens cosmography, and
quantify our results in terms of the uncertainty on the mean time delay
distance to a test sample of $N$ lenses (where for clarity each lens has the
same deflector and source redshift, and the same lens model and time delay
uncertainty).
